With great growth, comes greater Consumption: Energy consumption of countries around the world

### 2024-04-22 paper/paper.qmd
Initial datasheet info and clean up

Empirical studies have shown diverse results depending on the economic structure and developmental stage of the country in question. For developed nations, research has indicated a decoupling of energy consumption and economic growth, attributed to advances in energy efficiency and a shift towards service-oriented economies which are less energy-intensive [@OWEN-2006]. In contrast, developing countries tend to exhibit a strong correlation between energy consumption and GDP growth, driven by industrialization and infrastructure expansion which are highly energy-dependent (Bhattacharyya, 2011).

The policy implications of these findings are significant, as they influence national energy strategies and their alignment with economic objectives. The transition towards sustainable energy sources is also a critical factor in this equation, with renewable energy adoption seen as a key element in sustaining long-term economic growth without the environmental degradation associated with fossil fuels (Markandya et al., 2009).

Understanding the specific dynamics of energy consumption and economic growth within the context of a particular country requires a detailed examination of its economic policies, energy resources, and technological advancements. This paper aims to explore these themes within the context of countries globally, providing insights that may help in formulating strategies for sustainable economic and energy development.
Bhattacharyya, S. C. (2011). Energy Economics: Concepts, Issues, Markets, and Governance. London: Springer-Verlag.
Markandya, A., et al. (2009). What changes are needed in the way the financial markets allocate resources to sustainable energy. Energy Policy, 37(12), 4314-4317.

>>>>

Empirical studies have shown diverse results depending on the economic structure and developmental stage of the country in question. For developed nations, research has indicated a decoupling of energy consumption and economic growth, attributed to advances in energy efficiency and a shift towards service-oriented economies which are less energy-intensive [@OWEN-2006]. In contrast, developing countries tend to exhibit a strong correlation between energy consumption and GDP growth, driven by industrialization and infrastructure expansion which are highly energy-dependent [@Bhattacharyya-2019].

The policy implications of these findings are significant, as they influence national energy strategies and their alignment with economic objectives. The transition towards sustainable energy sources is also a critical factor in this equation, with renewable energy adoption seen as a key element in sustaining long-term economic growth without the environmental degradation associated with fossil fuels [@Wei-2023].

Understanding the specific dynamics of energy consumption and economic growth within the context of a particular country requires a detailed examination of its economic policies, energy resources, and technological advancements. This paper aims to explore these themes within the context of countries globally, providing insights that may help in formulating strategies for sustainable economic and energy development.
